% ─── REFERENCES ──────────────────────────────────────────────────────────────
\chapter*{References}
\addcontentsline{toc}{chapter}{References}

\begin{itemize}[label={}, leftmargin=1.5em, itemsep=0.3em]
  \item Greenhouse Gas Protocol (2023). \textit{Corporate Value Chain
    (Scope 3) Accounting and Reporting Standard}. World Resources
    Institute \& WBCSD.
  \item ISO 14040:2006\,/\,ISO 14044:2006. \textit{Environmental
    Management --- Life Cycle Assessment: Principles, Framework,
    Requirements and Guidelines}. International Organization for
    Standardization.
  \item International Energy Agency --- IEA (2023). \textit{CO$_2$
    Emissions from Fuel Combustion --- Highlights}. IEA Publications,
    Paris.
  \item Amazon Web Services (2023). \textit{AWS Sustainability Report
    2023}. Available at: \url{https://sustainability.aboutamazon.com}
  \item Microsoft (2023). \textit{Microsoft Environmental Sustainability
    Report 2023}. Available at:
    \url{https://www.microsoft.com/en-us/corporate-responsibility/sustainability}
  \item Accenture (2020). \textit{The Green Behind the Cloud}. Accenture
    Research. Available at:
    \url{https://www.accenture.com/us-en/insights/technology/green-behind-cloud}
  \item European Environment Agency (2023). \textit{Greenhouse Gas
    Emission Intensity of Electricity Generation in Europe}. EEA Report
    No.~16/2023.
  \item Uptime Institute (2023). \textit{Global Data Center Survey Results
    2023}. Uptime Institute, New York.
  \item European Commission (2016). \textit{General Data Protection
    Regulation (GDPR)}. Regulation (EU) 2016/679. Official Journal of
    the European Union.
  \item ITIL Foundation (2019). \textit{ITIL 4 Foundation}. Axelos
    Global Best Practice.
\end{itemize}

