
% ═══════════════════════════════════════════════════════════════════════════
%  SECTION 2.6 — ESG CRITERIA AND SUSTAINABILITY INDICATORS
% ═══════════════════════════════════════════════════════════════════════════

\chapter{Section 2.6 --- ESG Criteria and Sustainability Indicators}

The ESG (Environmental, Social, and Governance) framework constitutes a
transversal pillar of the Green ERP Migration project, embedded from the
earliest planning phases. Its purpose is to ensure that the migration
decision is not only financially justified, but also rigorously aligned with
contemporary sustainability standards and institutional obligations. ESG
criteria inform scope definition, vendor selection, risk assessment, and
post-deployment performance monitoring throughout the entire project
lifecycle.

\section{2.6.1 Environmental Criteria}

The primary environmental rationale for transitioning from an on-premise ERP
infrastructure to a cloud-based SaaS (Software as a Service) solution lies
in the material reduction of direct and indirect greenhouse gas (GHG)
emissions. GHG emissions --- primarily CO$_2$ and equivalent gases --- trap
solar radiation in the atmosphere and are the principal drivers of
anthropogenic climate change. Quantifying and minimising these emissions is
both a regulatory requirement and a core deliverable of this project.

\begin{itemize}[leftmargin=*, label=\textcolor{midgreen}{$\bullet$}]

  \item \textbf{Energy consumption reduction:} Physical on-premise servers
    operate continuously, drawing between 200 and 500 watts per unit.
    Migration to a shared hyperscale cloud environment --- where computing
    resources are dynamically allocated across a large user base --- is
    projected to reduce the organisation's per-unit energy consumption by
    30 to 40\%, owing to economies of scale and superior hardware
    utilisation rates.

  \item \textbf{GHG Emissions --- Scope 1, 2, and 3:} This project applies
    the \textbf{GHG Protocol} methodology, the internationally recognised
    standard for corporate greenhouse gas accounting. Emissions are
    classified into three categories:
    \begin{itemize}[label=\textcolor{lightgreen}{--}]
      \item \textit{Scope 1:} Direct emissions arising from company-owned
        or controlled sources (e.g., on-site generators or diesel backup
        systems).
      \item \textit{Scope 2:} Indirect emissions associated with the
        consumption of purchased electricity --- the dominant emission
        category for organisations operating dedicated server hardware.
      \item \textit{Scope 3:} All other indirect emissions across the
        value chain, including hardware manufacturing, logistics, and
        end-of-life disposal. These are substantially curtailed when the
        organisation ceases to own physical server assets.
    \end{itemize}

  \item \textbf{E-waste elimination:} Electronic waste (e-waste) refers to
    discarded equipment containing hazardous substances such as lead,
    mercury, and cadmium. The decommissioning of on-premise server
    infrastructure following migration eliminates the need for certified
    hardware disposal, reducing both environmental liability and associated
    compliance costs.

  \item \textbf{Power Usage Effectiveness (PUE):} PUE is a standardised
    metric quantifying the energy efficiency of a data centre, expressed as
    the ratio of total facility energy consumed to the energy delivered to
    computing equipment. A PUE of 1.0 represents perfect efficiency.
    On-premise facilities typically exhibit PUE values between 1.5 and
    2.0, reflecting significant energy losses to cooling and power
    distribution. Leading cloud providers consistently achieve PUE values
    in the range of 1.10 to 1.15.

  \item \textbf{Water Usage Effectiveness (WUE):} WUE measures the volume
    of water consumed per unit of IT load (litres per kilowatt-hour).
    Hyperscale cloud data centres deploy advanced adiabatic and liquid
    cooling systems that operate at substantially lower water consumption
    rates than conventional server room configurations.

\end{itemize}

\section{2.6.2 Social Criteria}

\begin{itemize}[leftmargin=*, label=\textcolor{midgreen}{$\bullet$}]

  \item \textbf{Enhanced accessibility and remote enablement:} A
    cloud-hosted ERP is accessible from any internet-connected device,
    regardless of location. This architecture natively supports remote and
    hybrid working arrangements, and removes barriers for employees with
    geographic or mobility constraints.

  \item \textbf{Continuous user experience improvement:} Cloud ERP
    platforms receive regular, vendor-managed updates delivering iterative
    interface improvements and new functionality without disruptive upgrade
    cycles, improving daily usability and contributing to measurable gains
    in operational productivity.

  \item \textbf{Digital capability development:} The migration programme
    incorporates a structured training curriculum covering all ERP user
    roles. This investment in workforce upskilling enhances employees'
    digital literacy and directly supports career development objectives at
    the organisational level.

  \item \textbf{Data privacy and GDPR compliance:} The General Data
    Protection Regulation (GDPR) --- Regulation (EU) 2016/679 ---
    establishes binding obligations for the collection, storage,
    processing, and transfer of personal data within the European Union.
    Full GDPR compliance is a non-negotiable requirement of this project,
    ensuring that both employee and customer data are handled with legal
    and ethical rigour.

  \item \textbf{IT workload redistribution:} Cloud service providers
    assume responsibility for infrastructure maintenance, security
    patching, and availability management. This structural shift releases
    internal IT personnel from repetitive operational tasks, enabling
    redeployment towards higher-value activities and improving overall
    working conditions.

\end{itemize}

\section{2.6.3 Governance Criteria}

\begin{itemize}[leftmargin=*, label=\textcolor{midgreen}{$\bullet$}]

  \item \textbf{Regulatory and standards compliance:}
    \begin{itemize}[label=\textcolor{lightgreen}{--}]
      \item \textbf{GDPR (Regulation EU 2016/679):} Mandatory compliance
        framework governing all personal data processing operations.
      \item \textbf{ISO 27001:} International standard specifying
        requirements for the establishment, implementation, and continual
        improvement of an Information Security Management System (ISMS).
      \item \textbf{ITIL v4:} The IT Infrastructure Library, fourth
        edition --- a globally recognised best-practice framework for IT
        service management that provides the operational governance model
        for this migration.
    \end{itemize}

  \item \textbf{Transparent ESG reporting:} A dedicated project dashboard
    consolidating ESG Key Performance Indicators (KPIs) will be maintained
    and distributed bi-weekly to all project stakeholders, ensuring
    accountability, facilitating early detection of deviations, and
    supporting informed decision-making at all governance levels.

  \item \textbf{Vendor accountability and ESG alignment:} The selected
    cloud service provider must demonstrate verifiable ESG commitments,
    including third-party renewable energy certifications and publicly
    disclosed annual sustainability reports. These requirements are
    incorporated into the vendor evaluation scorecard and contractual
    obligations.

  \item \textbf{Board-level ESG integration:} The project's GO\,/\,NO-GO
    decision, subject to approval by the Board of Directors, incorporates
    a mandatory ESG scorecard as a formal evaluation criterion, ensuring
    that sustainability performance is weighted alongside financial and
    technical factors at the highest level of project governance.

\end{itemize}

\section{2.6.4 ESG Key Performance Indicators (KPIs)}

The following table presents the comprehensive ESG KPI framework
established for this project. These indicators define measurable targets
across all three ESG pillars and will be monitored from project initiation
through post-deployment. Results will be reported bi-weekly via the project
dashboard (Section~8.2).

\vspace{0.5em}

\begin{longtable}{%
  p{2.2cm}
  p{3.5cm}
  p{2.2cm}
  p{2.2cm}
  p{3.0cm}}

\caption{ESG KPI Framework --- Green ERP Migration Project}
\label{tab:esg-kpi} \\

\rowcolor{headerrow}
\textcolor{white}{\textbf{Pillar}} &
\textcolor{white}{\textbf{KPI}} &
\textcolor{white}{\textbf{Baseline}} &
\textcolor{white}{\textbf{Target}} &
\textcolor{white}{\textbf{Method}} \\
\midrule
\endfirsthead

\rowcolor{headerrow}
\textcolor{white}{\textbf{Pillar}} &
\textcolor{white}{\textbf{KPI}} &
\textcolor{white}{\textbf{Baseline}} &
\textcolor{white}{\textbf{Target}} &
\textcolor{white}{\textbf{Method}} \\
\midrule
\endhead

\rowcolor{rowalt}
  Environmental &
  CO$_2$ Emissions (Scope~2) &
  $\sim$12\,t CO$_2$e/yr &
  $<$4\,t CO$_2$e/yr &
  Provider carbon report \\

  Environmental &
  CO$_2$ Emissions (Scope~3 --- hardware lifecycle) &
  $\sim$25\,t CO$_2$e total &
  $\sim$5\,t CO$_2$e total &
  LCA comparative analysis \\

\rowcolor{rowalt}
  Environmental &
  Annual Energy Consumption &
  $\sim$45{,}000\,kWh/yr &
  $<$30{,}000\,kWh/yr &
  Utility bills / cloud dashboard \\

  Environmental &
  Power Usage Effectiveness (PUE) &
  $\sim$1.80 &
  $\sim$1.15 &
  Published provider data \\

\rowcolor{rowalt}
  Environmental &
  E-waste Generated &
  $\sim$500\,kg (decommissioned servers) &
  $\sim$0\,kg &
  Asset inventory \\

  Social &
  User Satisfaction Score &
  3.1\,/\,5 &
  $\geq$4.2\,/\,5 &
  Post-migration survey \\

\rowcolor{rowalt}
  Social &
  Employees Trained &
  0\% &
  100\% of ERP users &
  Training completion records \\

  Social &
  Remote Access Availability &
  0\% &
  100\% (any device) &
  System access logs \\

\rowcolor{rowalt}
  Governance &
  GDPR Compliance &
  Partial &
  Full compliance &
  Audit report \\

  Governance &
  ISO~27001 Alignment &
  Not certified &
  Full alignment &
  Security assessment \\

\rowcolor{rowalt}
  Governance &
  ESG Reporting Frequency &
  None &
  Bi-weekly &
  Dashboard publication log \\

\bottomrule
\end{longtable}

\newpage

% ═══════════════════════════════════════════════════════════════════════════
%  LIFE CYCLE ASSESSMENT (LCA) --- ON-PREMISE vs. CLOUD SaaS
% ═══════════════════════════════════════════════════════════════════════════

\chapter{Life Cycle Assessment (LCA) --- On-Premise Servers vs.\ Cloud SaaS}

\section{Methodology and Standards}

A Life Cycle Assessment (LCA) is a structured environmental analysis
technique that quantifies the cumulative environmental impact of a product
or system across its entire operational lifespan --- from raw material
extraction (cradle) through to final decommissioning and disposal (grave).
In this project, the LCA serves as the analytical foundation for comparing
the environmental footprint of the current on-premise ERP server
infrastructure against the proposed cloud SaaS alternative.

The analysis is conducted in accordance with the following standards:
\begin{itemize}[label=\textcolor{midgreen}{$\bullet$}]
  \item \textbf{ISO 14040\,/\,ISO 14044} --- International standards
    defining the principles, framework, and requirements for conducting
    and reporting life cycle assessments.
  \item \textbf{GHG Protocol --- Scope 3 Standard} --- Applied to capture
    all indirect emissions across the value chain, with particular
    emphasis on hardware manufacturing and end-of-life disposal phases.
\end{itemize}

\section{LCA.1 --- Functional Unit and System Boundary}

\subsection{Functional Unit}

The functional unit defines the reference basis against which both
scenarios are evaluated, ensuring strict comparability:

\begin{quote}
\textit{Provision of integrated ERP system services --- encompassing user
management, supply chain, accounting, and HR modules --- to 50 concurrent
users over a continuous operational period of three years.}
\end{quote}

\subsection{System Boundary}

This study adopts a \textbf{cradle-to-grave} system boundary, encompassing
the following lifecycle phases:
\begin{itemize}[label=\textcolor{lightgreen}{--}]
  \item Raw material extraction and manufacturing of all server hardware
    components
  \item Transportation and on-site delivery of equipment
  \item Operational energy consumption across the 3-year service period
  \item Scheduled maintenance and component replacement activities
  \item End-of-life treatment: decommissioning, certified recycling, or
    controlled landfill disposal
\end{itemize}

\section{LCA.2 --- On-Premise Scenario: Inventory Analysis}

\subsection{Hardware Inventory}

The on-premise ERP infrastructure requires the following dedicated server
hardware components:

\vspace{0.5em}
\begin{tabularx}{\textwidth}{l c r X c}
\toprule
\rowcolor{headerrow}
\textcolor{white}{\textbf{Component}} &
\textcolor{white}{\textbf{Qty}} &
\textcolor{white}{\textbf{Power (W)}} &
\textcolor{white}{\textbf{Embodied CO$_2$ (kg)}} &
\textcolor{white}{\textbf{Lifespan}} \\
\midrule
\rowcolor{rowalt}
  Application Server (rack-mounted) & 2 & 350\,W ea. & 800\,kg ea. & 5 yrs \\
  Database Server                   & 1 & 400\,W     & 900\,kg     & 5 yrs \\
\rowcolor{rowalt}
  Network Switch                    & 2 & 80\,W ea.  & 50\,kg ea.  & 7 yrs \\
  UPS                               & 1 & 150\,W     & 200\,kg     & 5 yrs \\
\rowcolor{rowalt}
  Cooling\,/\,HVAC Unit             & 1 & 600\,W     & 300\,kg     & 10 yrs \\
  Storage Array (NAS)               & 1 & 120\,W     & 150\,kg     & 5 yrs \\
\bottomrule
\end{tabularx}
\captionof{table}{On-Premise Hardware Inventory}

\vspace{0.5em}
\textbf{Note on embodied carbon:} Embodied CO$_2$ denotes the cumulative
greenhouse gas emissions generated throughout the manufacturing process of
a device --- encompassing material extraction, component fabrication, and
assembly --- prior to any operational use.

\subsection{Operational Energy --- On-Premise}

Total installed hardware power draw: approximately \textbf{1{,}700\,W}
under continuous operation. Applying a \textbf{PUE of 1.8} --- reflecting
cooling overhead, UPS losses, and power distribution inefficiencies ---
across 8{,}760 annual operating hours:

\[
\text{Annual energy}
  = 1{,}700\,\mathrm{W} \times 1.8 \times 8{,}760\,\mathrm{h}
  = \mathbf{26{,}809\,\mathrm{kWh/year}}
\]

Applying the average European grid emission intensity of
\textbf{0.233\,kg\,CO$_2$e/kWh} (IEA, 2023):

\[
\text{Annual Scope\,2 CO}_{2}
  = 26{,}809 \times 0.233
  = \mathbf{6{,}246\,\mathrm{kg\,CO_2e/year}}
  \approx \mathbf{6.2\,\mathrm{t\,CO_2e/year}}
\]

\[
\text{3-year Scope\,2 total}
  = 6.2 \times 3
  = \mathbf{18.6\,\mathrm{t\,CO_2e}}
\]

\subsection{Scope 3 --- Hardware Manufacturing Emissions}

Embodied carbon is pro-rated to the 3-year project horizon on the basis of
the 5-year hardware design lifespan:

\[
\text{3-year embodied CO}_2
  = (800{\times}2 + 900 + 50{\times}2 + 200 + 300 + 150)\,\mathrm{kg}
    \times \frac{3}{5}
  = 3{,}250 \times 0.6
  = \mathbf{1{,}950\,\mathrm{kg\,CO_2e}}
\]

\subsection{Total On-Premise LCA Summary (3 Years)}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{X l r}
\toprule
\rowcolor{headerrow}
\textcolor{white}{\textbf{Lifecycle Phase}} &
\textcolor{white}{\textbf{GHG Scope}} &
\textcolor{white}{\textbf{CO$_2$e Emissions}} \\
\midrule
\rowcolor{rowalt} Hardware Manufacturing & Scope 3 (Upstream)   & $\sim$1{,}950\,kg \\
                  Transportation \& Logistics & Scope 3 (Upstream) & $\sim$100\,kg \\
\rowcolor{rowalt} Operational Energy (3 yrs) & Scope 2             & $\sim$18{,}600\,kg \\
                  Maintenance \& Components   & Scope 3             & $\sim$300\,kg \\
\rowcolor{rowalt} End-of-Life Disposal        & Scope 3 (Downstream)& $\sim$40\,kg \\
\midrule
\rowcolor{palegreen}
  \textbf{TOTAL (3-year period)} & \textbf{---} &
  $\mathbf{\sim\!21{,}000\,\mathrm{kg} \approx 21.0\,\mathrm{t\,CO_2e}}$ \\
\bottomrule
\end{tabularx}
\captionof{table}{On-Premise LCA Emissions Summary --- 3-Year Period}

\section{LCA.3 --- Cloud SaaS Scenario: Inventory Analysis}

In the cloud SaaS model, the organisation no longer procures or operates
dedicated server infrastructure. Computing resources are provisioned
on-demand by a hyperscale cloud provider (e.g., AWS, Microsoft Azure, or
Google Cloud Platform). The organisation's attributable environmental
impact is calculated as its proportional resource allocation within the
provider's shared, multi-tenant infrastructure.

\subsection{Key Modelling Assumptions}

\begin{itemize}[label=\textcolor{lightgreen}{--}]
  \item Cloud instance equivalent: 8\,vCPUs, 32\,GB RAM --- sufficient to
    replicate the on-premise ERP workload.
  \item Average CPU utilisation: 25--30\% (consistent with typical
    business ERP usage profiles).
  \item Cloud provider PUE: \textbf{1.12} (AWS published annual average,
    2023).
  \item Renewable energy coverage: \textbf{65--85\%} (based on hyperscale
    providers' published Power Purchase Agreements and renewable energy
    certificates).
  \item Effective grid emission intensity after renewable offset:
    $\sim$\textbf{0.08\,kg\,CO$_2$e/kWh}.
\end{itemize}

\subsection{Operational Energy --- Cloud}

Estimated workload power attributable to the organisation's share:
\textbf{180\,W} at 25\% CPU utilisation.

\[
\text{Annual cloud energy}
  = 180\,\mathrm{W} \times 1.12 \times 8{,}760\,\mathrm{h}
  = \mathbf{1{,}766\,\mathrm{kWh/year}}
\]

\[
\text{Annual Scope\,2 CO}_{2}
  = 1{,}766 \times 0.08
  = \mathbf{141\,\mathrm{kg\,CO_2e/year}}
\]

\[
\text{3-year Scope\,2 total}
  = 141 \times 3
  = \mathbf{423\,\mathrm{kg\,CO_2e}}
\]

\subsection{Total Cloud SaaS LCA Summary (3 Years)}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{X l r}
\toprule
\rowcolor{headerrow}
\textcolor{white}{\textbf{Lifecycle Phase}} &
\textcolor{white}{\textbf{GHG Scope}} &
\textcolor{white}{\textbf{CO$_2$e Emissions}} \\
\midrule
\rowcolor{rowalt} Hardware Manufacturing (proportional share) & Scope 3 (Upstream) & $\sim$150\,kg \\
                  Transportation \& Logistics & Scope 3 (Upstream) & $\sim$50\,kg \\
\rowcolor{rowalt} Operational Energy (3 yrs) & Scope 2             & $\sim$423\,kg \\
                  Maintenance \& Components   & Scope 3             & $\sim$30\,kg \\
\rowcolor{rowalt} End-of-Life (provider-managed) & Scope 3 (Downstream) & $<$10\,kg \\
\midrule
\rowcolor{palegreen}
  \textbf{TOTAL (3-year period)} & \textbf{---} &
  $\mathbf{\sim\!663\,\mathrm{kg} \approx 0.66\,\mathrm{t\,CO_2e}}$ \\
\bottomrule
\end{tabularx}
\captionof{table}{Cloud SaaS LCA Emissions Summary --- 3-Year Period}

\section{LCA.4 --- Comparative Results}

\vspace{0.5em}
\begin{tabularx}{\textwidth}{X r r r r}
\toprule
\rowcolor{headerrow}
\textcolor{white}{\textbf{Environmental Category}} &
\textcolor{white}{\textbf{On-Premise}} &
\textcolor{white}{\textbf{Cloud SaaS}} &
\textcolor{white}{\textbf{Reduction}} &
\textcolor{white}{\textbf{\%}} \\
\midrule
\rowcolor{rowalt}
  Total CO$_2$e (3 yrs)      & $\sim$21{,}000\,kg & $\sim$663\,kg    & 20{,}337\,kg & \textbf{96.8\%} \\
  Total Energy Consumption   & $\sim$80{,}400\,kWh& $\sim$5{,}300\,kWh& 75{,}100\,kWh & \textbf{93.4\%} \\
\rowcolor{rowalt}
  Embodied Carbon (hardware) & $\sim$1{,}950\,kg  & $\sim$150\,kg    & 1{,}800\,kg  & \textbf{92.3\%} \\
  E-waste Generated          & $\sim$500\,kg      & $\sim$0\,kg      & 500\,kg      & \textbf{100\%}  \\
\rowcolor{rowalt}
  Average PUE                & 1.80               & 1.12             & 0.68         & \textbf{37.8\%} \\
\bottomrule
\end{tabularx}
\captionof{table}{LCA Comparative Results --- On-Premise vs.\ Cloud SaaS (3-Year Period)}

\vspace{0.5em}

\subsection{Key Findings and Interpretation}

\begin{itemize}[label=\textcolor{midgreen}{$\bullet$}]

  \item The cloud SaaS scenario achieves a \textbf{total CO$_2$e reduction
    of 96.8\%} over the three-year assessment period, reducing lifecycle
    emissions from approximately 21 tonnes to under 0.7 tonnes.

  \item \textbf{Operational energy (Scope~2) is the dominant emission
    driver} in the on-premise scenario, representing 88.6\% of total
    lifecycle emissions. This is substantially mitigated through the cloud
    provider's superior PUE and high renewable energy coverage.

  \item \textbf{Scope~3 embodied carbon is reduced by over 92\%} as a
    direct consequence of the shared infrastructure model: hardware
    manufacturing emissions are distributed across thousands of concurrent
    customers, reducing the per-organisation attribution to a negligible
    level.

  \item \textbf{E-waste liability is entirely eliminated}: the organisation
    assumes no responsibility for the procurement, maintenance, or
    certified disposal of server-grade hardware under the cloud model.

  \item These findings are consistent with established industry benchmarks.
    Research by Accenture (2020) demonstrates that migrating on-premise
    enterprise workloads to public cloud infrastructure reduces CO$_2$
    emissions by 84 to 98\%, contingent on the provider's energy mix and
    workload consolidation efficiency.

\end{itemize}

\newpage