\chapter{Scope Management -- WBS, WBS Dictionary \& RTM}

% ─────────────────────────────────────────────────────────────
\section{Work Breakdown Structure (WBS)}

The Work Breakdown Structure (WBS) is the foundational scope management artifact of the ERP
migration project. Following the PMBoK deliverable-oriented decomposition principle, the WBS
organizes the entire project into a hierarchical structure of work packages. Each work package is
clearly bounded, assigned to a responsible owner, linked to a measurable deliverable, and
traceable to both the Gantt schedule and the project budget.

The WBS is structured around six major phases reflecting the project lifecycle: Initiation, Scope
Planning, Planning, Migration, Deployment, and Closure. This structure ensures logical
sequencing, prevents scope creep, and provides the baseline against which all progress is
measured.

\medskip
\noindent\textbf{Key Principles Applied:}
\begin{itemize}
    \item \textbf{Deliverable-oriented:} each work package produces a tangible, verifiable output.
    \item \textbf{Non-overlapping:} no two work packages share the same scope or deliverable.
    \item \textbf{100\% Rule:} the WBS covers the complete scope — nothing is missing or duplicated.
    \item \textbf{Traceable:} all work packages are linked to Gantt activities, budget lines, and RTM requirements.
    \item \textbf{ESG-integrated:} sustainability tasks (LCA, ESG KPIs) are embedded within the migration and deployment phases.
\end{itemize}

% ── Table 4.1 ────────────────────────────────────────────────
\begin{table}[H]
\centering
\caption{WBS Overview by Phase}
\label{tab:wbs-overview}
\arrayrulecolor{tableborder}
\renewcommand{\arraystretch}{1.7}
\small
\begin{tabular}{|>{\bfseries}p{1.6cm}|p{3.0cm}|p{5.2cm}|p{1.8cm}|p{1.5cm}|p{1.2cm}|}
\hline
\rowcolor{tableheader}
\textbf{WBS Code} &
\textbf{Work Package} &
\textbf{Main Deliverable} &
\textbf{Timeline} &
\textbf{Duration} &
\textbf{Budget \%} \\
\hline
1.0 & Initiation & Project Charter (Scope, Objectives, ESG Vision, Stakeholders) & Weeks 1--2 & 2 weeks & 4\% \\
\hline
2.0 & Scope Planning & WBS + RTM (Requirements traceability and project decomposition) & Weeks 3--5 & 3 weeks & 6\% \\
\hline
3.0 & Planning & Gantt Schedule + Budget Baseline (cost \& time estimation) & Weeks 6--7 & 2 weeks & 5\% \\
\hline
4.0 & Migration & SaaS ERP Deployment (data migration + configuration + testing) & Weeks 8--19 & 12 weeks & 54\% \\
\hline
5.0 & Deployment & Go-Live + User Training + Stabilization Phase & Weeks 20--23 & 4 weeks & 19\% \\
\hline
6.0 & Closure & Final Project Report + Lessons Learned (REX) & Week 24 & 1 week & 3\% \\
\hline
\end{tabular}
\end{table}

\noindent\textbf{Interpretation:}
\begin{itemize}
    \item The \textbf{Initiation phase (1.0)} defines the project governance framework and produces the signed Project Charter.
    \item The \textbf{Scope Planning phase (2.0)} produces the WBS and RTM — the two core scope control artifacts.
    \item The \textbf{Planning phase (3.0)} establishes the baseline for schedule, budget, risk, quality, and communication.
    \item The \textbf{Migration phase (4.0)} is the largest phase (54\% of budget) and represents the core technical execution of the ERP transformation.
    \item The \textbf{Deployment phase (5.0)} ensures operational transition through training, Go-Live, and stabilization.
    \item The \textbf{Closure phase (6.0)} formalizes project completion, captures lessons learned, and hands over governance to operations.
\end{itemize}

% ── Table 4.2 ────────────────────────────────────────────────
% ── Table 4.2: Detailed WBS (Converted to longtable) ──────────
\renewcommand{\arraystretch}{1.3}
\scriptsize
\arrayrulecolor{tableborder}
\begin{longtable}{|>{\bfseries}p{1.1cm}|p{3.4cm}|p{3.1cm}|p{2.2cm}|p{1.0cm}|p{1.4cm}|p{0.8cm}|}
    
    % --- Table Caption & Label ---
    \caption{Detailed WBS -- All Work Packages} \label{tab:wbs-detailed} \\
    
    % --- First Page Header ---
    \hline
    \rowcolor{tableheader}
    \textbf{Code} & \textbf{Work Package Name} & \textbf{Deliverable} & \textbf{Owner} & \textbf{Dur.} & \textbf{Cost (TND)} & \textbf{Bdgt} \\
    \hline
    \endfirsthead
    
    % --- Subsequent Page Headers (Repeating) ---
    \hline
    \rowcolor{tableheader}
    \multicolumn{7}{|c|}{\textit{Continued from previous page}} \\
    \hline
    \rowcolor{tableheader}
    \textbf{Code} & \textbf{Work Package Name} & \textbf{Deliverable} & \textbf{Owner} & \textbf{Dur.} & \textbf{Cost (TND)} & \textbf{Bdgt} \\
    \hline
    \endhead

    % --- Footer for pages where table continues ---
    \hline
    \multicolumn{7}{|r|}{\textit{Continued on next page...}} \\
    \hline
    \endfoot

  % --- Final Footer ---
  \hline
  \endlastfoot

    % ── Phase 1 ──
    \rowcolor{tableheader}
    1.0 & \textbf{INITIATION} & Project Charter & Project Manager & 2 wks & 12{,}000 & 4\% \\
    \hline
    1.1 & Define Business Context \& Need & Problem Statement, ESG Vision & Business Analyst & 3 days & 2{,}500 & \\
    \hline
    1.2 & Identify \& Analyze Stakeholders & Stakeholder Register & Project Manager & 3 days & 1{,}500 & \\
    \hline
    1.3 & Draft Project Charter & Approved Charter Document & Project Manager & 4 days & 3{,}000 & \\
    \hline
    1.4 & Define Scope Boundaries & In-Scope / Out-of-Scope Statement & Business Analyst + PM & 2 days & 2{,}000 & \\
    \hline
    1.5 & Define SMART Objectives \& KPIs & Objectives Matrix + KPI Framework & Project Manager & 2 days & 2{,}000 & \\
    \hline
    1.6 & Charter Approval (GO Gate 1) & Signed Charter & Steering Committee & 1 day & 1{,}000 & \\
    \hline

    % ── Phase 2 ──
    \rowcolor{tableheader}
    2.0 & \textbf{SCOPE PLANNING} & WBS + RTM & WBS Manager & 3 wks & 18{,}000 & 6\% \\
    \hline
    2.1 & Map Existing ERP Processes (AS-IS) & AS-IS Process Map & Business Analyst & 5 days & 4{,}000 & \\
    \hline
    2.2 & Define Future State (TO-BE) & TO-BE Architecture & Business Analyst + CIO & 3 days & 3{,}000 & \\
    \hline
    2.3 & Build Detailed WBS & WBS Diagram + Work Packages & WBS Manager & 4 days & 3{,}500 & \\
    \hline
    2.4 & Draft WBS Dictionary & WBS Dictionary (all work packages) & WBS Manager & 4 days & 3{,}500 & \\
    \hline
    2.5 & Build Requirements Traceability Matrix (RTM) & RTM (all REQ linked to WBS) & WBS Manager + BA & 5 days & 4{,}000 & \\
    \hline

    % ── Phase 3 ──
    \rowcolor{tableheader}
    3.0 & \textbf{PLANNING} & Gantt + Budget Baseline & Planner + Finance & 2 wks & 15{,}000 & 5\% \\
    \hline
    3.1 & Build Gantt Chart \& CPM & Gantt Diagram + Critical Path & Planner & 3 days & 3{,}000 & \\
    \hline
    3.2 & Estimate Budget \& Resources & Budget Baseline & Finance Manager & 3 days & 3{,}000 & \\
    \hline
    3.3 & Develop Risk Register & Risk Register (probability/impact) & Quality \& Risk Manager & 2 days & 2{,}500 & \\
    \hline
    3.4 & Develop Communication Plan & Communication Plan & Quality \& Risk Manager & 2 days & 2{,}000 & \\
    \hline
    3.5 & Develop Quality Plan & Quality Plan (ISO, GDPR) & Quality \& Risk Manager & 2 days & 2{,}500 & \\
    \hline
    3.6 & Baseline Approval (GO Gate 2) & Approved Planning Baseline & Steering Committee & 1 day & 2{,}000 & \\
    \hline

    % ── Phase 4 ──
    \rowcolor{tableheader}
    4.0 & \textbf{MIGRATION (ERP SaaS)} & SaaS ERP Deployed & Integrator + CIO & 12 wks & 155{,}000 & 54\% \\
    \hline
    4.1 & ERP Environment Setup (Cloud) & Cloud Infrastructure Ready & CIO + Vendor & 5 days & 15{,}000 & \\
    \hline
    4.2 & Data Extraction \& Cleaning & Cleaned \& Validated Data Sets & Integrator & 10 days & 20{,}000 & \\
    \hline
    4.3 & Data Migration (HR, Finance, Procurement) & Migrated Data in SaaS ERP & Integrator & 15 days & 30{,}000 & \\
    \hline
    4.4 & ERP Configuration \& Customization & Configured ERP Modules & Integrator + Vendor & 12 days & 25{,}000 & \\
    \hline
    4.5 & API Integration (CRM, BI Tools) & Tested API Connections & Integrator & 8 days & 15{,}000 & \\
    \hline
    4.6 & Security \& GDPR Configuration & Compliance Report (GDPR, ISO 27001) & CISO + Integrator & 7 days & 15{,}000 & \\
    \hline
    4.7 & Unit \& Integration Testing & Test Reports (Pass/Fail) & Integrator + QA & 10 days & 18{,}000 & \\
    \hline
    4.8 & UAT -- User Acceptance Testing & UAT Sign-off ($\geq$95\% acceptance) & Business Teams + PM & 10 days & 12{,}000 & \\
    \hline
    4.9 & Migration Approval (GO Gate 3) & Migration Validated & Steering Committee & 1 day & 5{,}000 & \\
    \hline

    % ── Phase 5 ──
    \rowcolor{tableheader}
    5.0 & \textbf{DEPLOYMENT \& STABILIZATION} & ERP Live + Users Trained & PM + Vendor & 4 wks & 55{,}000 & 19\% \\
    \hline
    5.1 & User Training Program & Training Materials + Sessions & PM + Business Teams & 8 days & 12{,}000 & \\
    \hline
    5.2 & Go-Live Execution & ERP System Live & CIO + Vendor & 2 days & 10{,}000 & \\
    \hline
    5.3 & Post Go-Live Monitoring & Incident Log + SLA Report & Vendor + CIO & 10 days & 15{,}000 & \\
    \hline
    5.4 & Business Continuity \& DRP & BCP/DRP Plan Activated & CISO + PM & 5 days & 10{,}000 & \\
    \hline
    5.5 & ESG \& LCA Assessment (Post-Migration) & CO$_2$ Reduction Report & ESG Manager & 5 days & 8{,}000 & \\
    \hline

    % ── Phase 6 ──
    \rowcolor{tableheader}
    6.0 & \textbf{CLOSURE} & Final Report + REX & Project Manager & 1 wk & 10{,}000 & 3\% \\
    \hline
    6.1 & Final Performance Report & KPI Dashboard Final Report & PM & 3 days & 4{,}000 & \\
    \hline
    6.2 & Lessons Learned (REX) & REX Document & PM + Team & 2 days & 3{,}000 & \\
    \hline
    6.3 & Project Closure \& Handover & Signed Closure Report & Steering Committee & 1 day & 3{,}000 & \\
    \hline
\end{longtable}


\noindent Each WBS work package is mapped to a corresponding activity in the Gantt schedule
(Section~5), ensuring full alignment between scope and timeline.

% ─────────────────────────────────────────────────────────────
\section{WBS Dictionary}

The WBS Dictionary provides a complete and formal description of each work package identified in
the WBS. It defines the scope, deliverables, ownership, acceptance criteria, dependencies, and
cost for each package. This document serves as the execution reference for all project team
members and ensures no ambiguity in task responsibilities. Selected work packages are detailed
below, covering all six project phases.

\medskip
\noindent\textit{Note: The WBS numbering follows a hierarchical structure rather than a
chronological order, reflecting the decomposition of project phases.}
\medskip

% ── Dictionary macros ─────────────────────────────────────────
\newcommand{\wbsentry}[3]{%
  \vspace{6pt}
  \noindent{\bfseries Work Package #1 -- #2}
  \vspace{4pt}

  \arrayrulecolor{tableborder}
  \renewcommand{\arraystretch}{1.55}
  \begin{tabular}{|>{\bfseries\raggedright\arraybackslash}p{3.6cm}|p{11.0cm}|}
  \hline
  #3
  \hline
  \end{tabular}
  \vspace{10pt}
}

\newcommand{\wbsrow}[2]{#1 & #2 \\ \hline}
\newcommand{\wbsrowa}[2]{#1 & #2 \\ \hline}

% ── WP 1.1 ───────────────────────────────────────────────────
\wbsentry{1.1}{Define Business Context \& Need}{%
  \wbsrow{Description}{Analyze the current On-Premise ERP environment, identify limitations, and document the business justification for the SaaS migration. This forms the foundation for the Project Charter.}
  \wbsrowa{Main Deliverable}{Problem Statement, ESG Vision Document}
  \wbsrow{Responsible Owner}{Business Analyst}
  \wbsrowa{Inputs}{Existing ERP documentation, business process inventory}
  \wbsrow{Outputs}{Validated problem statement and strategic rationale}
  \wbsrowa{Acceptance Criteria}{Approved by Project Manager and General Management}
  \wbsrow{Estimated Duration}{3 days}
  \wbsrowa{Estimated Cost}{2{,}500 TND}
  \wbsrow{Dependencies}{None -- first work package}
  \wbsrowa{Key Risk}{Incomplete process documentation may delay analysis}
}

% ── WP 1.3 ───────────────────────────────────────────────────
\wbsentry{1.3}{Draft Project Charter}{%
  \wbsrow{Description}{Produce the formal Project Charter including the purpose statement, project scope, hypotheses, SMART objectives, constraints, ESG criteria, and governance structure. This is the primary governance artifact for Phase~1.}
  \wbsrowa{Main Deliverable}{Approved Project Charter Document}
  \wbsrow{Responsible Owner}{Project Manager}
  \wbsrowa{Inputs}{Problem statement (1.1), stakeholder register (1.2)}
  \wbsrow{Outputs}{Signed and approved Project Charter}
  \wbsrowa{Acceptance Criteria}{Approved by Steering Committee at GO Gate~1}
  \wbsrow{Estimated Duration}{4 days}
  \wbsrowa{Estimated Cost}{3{,}000 TND}
  \wbsrow{Dependencies}{1.1, 1.2}
  \wbsrowa{Key Risk}{Scope disagreements between stakeholders may require revision cycles}
}

% ── WP 2.3 ───────────────────────────────────────────────────
\wbsentry{2.3}{Build Detailed WBS}{%
  \wbsrow{Description}{Decompose the full project into hierarchical work packages using a deliverable-oriented approach. The WBS is structured into 6 main phases and 30+ sub-packages, each linked to a Gantt activity, budget line, and RTM requirement.}
  \wbsrowa{Main Deliverable}{WBS Diagram (hierarchical) + Work Package List}
  \wbsrow{Responsible Owner}{WBS Manager (Hanine)}
  \wbsrowa{Inputs}{Validated scope (1.4), AS-IS/TO-BE process maps (2.1, 2.2)}
  \wbsrow{Outputs}{Complete WBS structure serving as baseline for planning}
  \wbsrowa{Acceptance Criteria}{Covers 100\% of scope; no overlap between work packages; validated by PM}
  \wbsrow{Estimated Duration}{4 days}
  \wbsrowa{Estimated Cost}{3{,}500 TND}
  \wbsrow{Dependencies}{2.1, 2.2}
  \wbsrowa{Key Risk}{Incomplete scope understanding may cause missing work packages}
}

% ── WP 2.4 ───────────────────────────────────────────────────
\wbsentry{2.4}{Draft WBS Dictionary}{%
  \wbsrow{Description}{Document each work package with full details: description, deliverable, owner, inputs/outputs, acceptance criteria, duration, cost, and dependencies. The dictionary is the reference artifact for project execution control.}
  \wbsrowa{Main Deliverable}{WBS Dictionary (complete -- all work packages)}
  \wbsrow{Responsible Owner}{WBS Manager (Hanine)}
  \wbsrowa{Inputs}{WBS structure (2.3)}
  \wbsrow{Outputs}{Detailed work package descriptions used by all team members}
  \wbsrowa{Acceptance Criteria}{All work packages documented; validated by PM and team}
  \wbsrow{Estimated Duration}{4 days}
  \wbsrowa{Estimated Cost}{3{,}500 TND}
  \wbsrow{Dependencies}{2.3}
  \wbsrowa{Key Risk}{Resource and cost misestimations at this stage propagate to budget}
}

% ── WP 2.5 ───────────────────────────────────────────────────
\wbsentry{2.5}{Build Requirements Traceability Matrix (RTM)}{%
  \wbsrow{Description}{Link all business requirements to their corresponding WBS work packages, validation method, and KPI. The RTM ensures no requirement is lost during execution and supports GO/NO-GO decision-making at each project gate.}
  \wbsrowa{Main Deliverable}{RTM document -- all REQ linked to WBS + KPI}
  \wbsrow{Responsible Owner}{WBS Manager + Business Analyst}
  \wbsrowa{Inputs}{Business requirements (from 2.1, 2.2), WBS (2.3)}
  \wbsrow{Outputs}{RTM used as testing baseline and scope validation artifact}
  \wbsrowa{Acceptance Criteria}{100\% of requirements traced; validated by PM and Steering Committee}
  \wbsrow{Estimated Duration}{5 days}
  \wbsrowa{Estimated Cost}{4{,}000 TND}
  \wbsrow{Dependencies}{2.3, 2.4}
  \wbsrowa{Key Risk}{Missing or ambiguous requirements lead to incomplete test coverage}
}

% ── WP 4.3 ───────────────────────────────────────────────────
\wbsentry{4.3}{Data Migration (HR, Finance, Procurement)}{%
  \wbsrow{Description}{Execute the extraction, transformation, and loading (ETL) of all ERP data from the On-Premise system to the SaaS Cloud platform. Covers three core modules: HR (payroll, leave, recruitment), Finance (accounting, invoicing, reporting), and Procurement (orders, suppliers, contracts).}
  \wbsrowa{Main Deliverable}{Migrated and validated data sets in SaaS ERP}
  \wbsrow{Responsible Owner}{Migration Integrator}
  \wbsrowa{Inputs}{Cleaned data (4.2), configured SaaS environment (4.1)}
  \wbsrow{Outputs}{All historical and active data available in cloud ERP}
  \wbsrowa{Acceptance Criteria}{Zero data loss; 100\% data integrity validated by business teams}
  \wbsrow{Estimated Duration}{15 days}
  \wbsrowa{Estimated Cost}{30{,}000 TND}
  \wbsrow{Dependencies}{4.1, 4.2}
  \wbsrowa{Key Risk}{Data inconsistency; encoding issues; volume exceeding migration window}
}

% ── WP 4.8 ───────────────────────────────────────────────────
\wbsentry{4.8}{UAT -- User Acceptance Testing}{%
  \wbsrow{Description}{Conduct structured User Acceptance Testing with representatives from all business units (HR, Finance, Procurement). UAT scenarios are based on the RTM and must achieve $\geq$95\% functional acceptance before Go-Live authorization.}
  \wbsrowa{Main Deliverable}{UAT test reports + Sign-off document}
  \wbsrow{Responsible Owner}{Business Teams + Project Manager}
  \wbsrowa{Inputs}{Configured ERP (4.4), trained users (5.1 partial), test scenarios from RTM}
  \wbsrow{Outputs}{Signed UAT acceptance document; defect closure report}
  \wbsrowa{Acceptance Criteria}{$\geq$95\% functional acceptance rate; all critical defects resolved}
  \wbsrow{Estimated Duration}{10 days}
  \wbsrowa{Estimated Cost}{12{,}000 TND}
  \wbsrow{Dependencies}{4.3, 4.4, 4.5, 4.6, 4.7}
  \wbsrowa{Key Risk}{Low user adoption; unexpected bugs requiring rework cycles}
}

% ── WP 5.1 ───────────────────────────────────────────────────
\wbsentry{5.1}{User Training Program}{%
  \wbsrow{Description}{Design and deliver role-based training sessions for all ERP end users across HR, Finance, and Procurement departments. Training must be completed before Go-Live and achieve 100\% completion rate.}
  \wbsrowa{Main Deliverable}{Training materials (manuals, e-learning) + attendance records}
  \wbsrow{Responsible Owner}{Project Manager + Business Teams}
  \wbsrowa{Inputs}{Configured ERP modules, user role mapping}
  \wbsrow{Outputs}{100\% of users trained and certified for their role}
  \wbsrowa{Acceptance Criteria}{100\% training completion; user satisfaction score $\geq$7/10}
  \wbsrow{Estimated Duration}{8 days}
  \wbsrowa{Estimated Cost}{12{,}000 TND}
  \wbsrow{Dependencies}{4.4, 4.8}
  \wbsrowa{Key Risk}{Scheduling conflicts; low engagement from end users}
}

% ─────────────────────────────────────────────────────────────
\section{Requirements Traceability Matrix (RTM)}

The Requirements Traceability Matrix (RTM) is a critical project governance artifact that ensures
end-to-end traceability between business needs and project deliverables. Each requirement is
linked to its corresponding WBS work package, validation method, measurable KPI, and current
status.

The RTM is used throughout the project lifecycle to validate complete functional coverage,
support structured testing during the UAT phase, enable data-driven GO/NO-GO decisions at
milestone gates, and maintain alignment between scope, execution, and performance indicators.

\medskip
\noindent\textbf{RTM Priority Classification (MoSCoW method):}
\begin{itemize}
    \item \textbf{\textcolor{musthave}{Must Have:}} critical requirements whose failure would block Go-Live.
    \item \textbf{\textcolor{shouldhave}{Should Have:}} high-value requirements that significantly improve project success.
    \item \textbf{\textcolor{couldhave}{Could Have:}} desirable enhancements included if resources and time permit.
\end{itemize}

% ── Table 4.3 ────────────────────────────────────────────────
\begin{table}[H]
\centering
\caption{Full Requirements Traceability Matrix (RTM)}
\label{tab:rtm}
\arrayrulecolor{tableborder}
\renewcommand{\arraystretch}{1.65}
\scriptsize
\begin{tabular}{|p{1.1cm}|p{3.2cm}|p{1.8cm}|p{0.9cm}|p{2.8cm}|p{2.6cm}|p{1.2cm}|}
\hline

\textbf{REQ ID} &
\textbf{Requirement} &
\textbf{Priority} &
\textbf{WBS} &
\textbf{Validation Method} &
\textbf{KPI / Success Criterion} &
\textbf{Status} \\
\hline

REQ-01 & HR Module Migration (Payroll, Leave, Recruitment) &
\cellcolor{musthavebg}\textbf{\textcolor{musthave}{Must Have}} &
4.3 & UAT HR Test Suite & $\geq$95\% functional coverage & Pending UAT \\
\hline

REQ-02 & Finance Module Migration (Accounting, Invoicing) &
\cellcolor{musthavebg}\textbf{\textcolor{musthave}{Must Have}} &
4.3 & UAT Finance Tests & 100\% critical processes validated & Pending UAT \\
\hline

REQ-03 & Procurement Module Migration (Orders, Suppliers) &
\cellcolor{musthavebg}\textbf{\textcolor{musthave}{Must Have}} &
4.3 & UAT Procurement Tests & $\geq$95\% functional coverage & Pending UAT \\
\hline

REQ-04 & Cloud Infrastructure Setup \& Configuration &
\cellcolor{musthavebg}\textbf{\textcolor{musthave}{Must Have}} &
4.1 & Infrastructure readiness review & Environment available Week~8 & In Planning \\
\hline

REQ-05 & GDPR Compliance for All Migrated Data &
\cellcolor{musthavebg}\textbf{\textcolor{musthave}{Must Have}} &
4.6 & Security \& Compliance Audit & 0 critical non-compliance issues & In Planning \\
\hline

REQ-06 & SaaS Availability $\geq$99.5\% (SLA) &
\cellcolor{musthavebg}\textbf{\textcolor{musthave}{Must Have}} &
5.2 & SLA Monitoring \& Stress Testing & $\geq$99.5\% uptime post Go-Live & Post Go-Live \\
\hline

REQ-07 & Reduce IT Operational Costs by 30\% (3yr TCO) &
\cellcolor{shouldhavebg}\textbf{\textcolor{shouldhave}{Should Have}} &
3.2 & Financial Tracking (CPI Analysis) & CPI $\geq$ 0.95 & Ongoing \\
\hline

REQ-08 & 100\% User Training Completion Before Go-Live &
\cellcolor{musthavebg}\textbf{\textcolor{musthave}{Must Have}} &
5.1 & Training Attendance \& Certification & 100\% trained users & Pre Go-Live \\
\hline

REQ-09 & Reduce CO$_2$ Emissions by 40\% (LCA Scope~3) &
\cellcolor{shouldhavebg}\textbf{\textcolor{shouldhave}{Should Have}} &
5.5 & Life Cycle Assessment (LCA Study) & $-$40\% CO$_2$ vs On-Premise & Post Migration \\
\hline

REQ-10 & API Integration with CRM / BI Tools &
\cellcolor{couldhavebg}\textbf{\textcolor{couldhave}{Could Have}} &
4.5 & Integration Testing (API Response Rate) & API Success Rate $\geq$98\% & In Testing \\
\hline

REQ-11 & Business Continuity \& DRP Plan Activated &
\cellcolor{musthavebg}\textbf{\textcolor{musthave}{Must Have}} &
5.4 & BCP/DRP drill \& documentation review & RTO $\leq$4h; RPO $\leq$1h & Pre Go-Live \\
\hline

REQ-12 & Data Integrity Validation Post-Migration &
\cellcolor{musthavebg}\textbf{\textcolor{musthave}{Must Have}} &
4.3 & Data reconciliation report & 0\% data loss; 100\% record match & Post Migration \\
\hline

REQ-13 & ISO 27001 Alignment for Security Controls &
\cellcolor{shouldhavebg}\textbf{\textcolor{shouldhave}{Should Have}} &
4.6 & Security controls audit checklist & ISO 27001 gap score $\leq$5\% & In Planning \\
\hline

REQ-14 & Project KPI Dashboard Operational at Go-Live &
\cellcolor{shouldhavebg}\textbf{\textcolor{shouldhave}{Should Have}} &
6.1 & Dashboard review by Steering Committee & All KPIs visible and updated & Pre-Closure \\
\hline

\end{tabular}
\end{table}

\medskip
\noindent\textbf{RTM Governance Rules:}
\begin{itemize}
    \item Any new requirement must be formally submitted through a Change Request (CR) process.
    \item All \textit{Must Have} requirements must reach ``Validated'' status before the Steering Committee issues a GO for Go-Live.
    \item The RTM is reviewed at each project gate (GO Gate~1, 2, 3) and updated continuously during UAT.
    \item The WBS Manager (Hanine) maintains the RTM in collaboration with the Business Analyst and Quality Manager.
\end{itemize}

\medskip


\vspace{12pt}