
% ═══════════════════════════════════════════════════════════════════════════
%  SECTION 7 --- ENERGY COSTS IN THE LIFE CYCLE COST ANALYSIS
%  ESG Team Contribution
% ═══════════════════════════════════════════════════════════════════════════

\chapter{Section 7 --- Energy Costs in the Life Cycle Cost Analysis}

\section{Life Cycle Costing: Scope and Purpose}

Life Cycle Costing (LCC) is a financial evaluation methodology that
determines the \textit{total cost of ownership} of a system across its
complete operational lifespan, rather than assessing acquisition costs in
isolation. LCC aggregates all expenditure categories --- including capital
investment, energy consumption, maintenance, operational overheads, and
end-of-life decommissioning --- into a unified cost model that enables
rigorous comparison between infrastructure alternatives.

This section constitutes the \textbf{ESG team's formal contribution to the
Finance team's LCC model}: it provides the quantified energy cost inputs
for both the on-premise and cloud SaaS scenarios, derived directly from the
Life Cycle Assessment (LCA) findings documented in Section~2.6. These
figures feed into the Total Cost of Ownership (TCO) comparative analysis
presented in Section~7.6 of the main project report.

\section{7.1 On-Premise Energy Costs}

The on-premise energy cost model encompasses all direct electricity
expenditures associated with the operation of dedicated server hardware,
including associated infrastructure overhead (cooling, power conditioning,
and uninterruptible power supply systems). Annual consumption figures are
derived from the LCA hardware inventory and operational energy calculations
(Section~2.6, LCA.2).

\vspace{0.5em}
\begin{tabularx}{\textwidth}{X r r}
\toprule
\rowcolor{headerrow}
\textcolor{white}{\textbf{Cost Component}} &
\textcolor{white}{\textbf{Annual Cost (\texteuro{})}} &
\textcolor{white}{\textbf{3-Year Total (\texteuro{})}} \\
\midrule
\rowcolor{rowalt}
  Server electricity (26{,}809\,kWh $\times$ \texteuro{}0.12/kWh)
  & \texteuro{}3{,}217 & \texteuro{}9{,}651 \\
  HVAC and cooling system overhead
  & \texteuro{}800    & \texteuro{}2{,}400 \\
\rowcolor{rowalt}
  UPS and power conditioning losses
  & \texteuro{}200    & \texteuro{}600 \\
\midrule
\rowcolor{palegreen}
  \textbf{TOTAL --- On-Premise Energy}
  & \textbf{\texteuro{}4{,}217/year} & \textbf{\texteuro{}12{,}651} \\
\bottomrule
\end{tabularx}
\captionof{table}{On-Premise Energy Cost Summary --- 3-Year Assessment Period}

\vspace{0.5em}
\textbf{Notes:} The electricity tariff of \texteuro{}0.12/kWh reflects the
applicable commercial rate consistent with 2023 European energy pricing
benchmarks (IEA, 2023). HVAC and UPS figures are derived from the hardware
power inventory in Section~2.6 (Table~LCA.1).

\section{7.2 Cloud SaaS Energy Costs}

In the cloud SaaS operating model, energy costs are structurally embedded
within the monthly subscription fee negotiated with the cloud service
provider. The organisation no longer incurs separate, direct electricity
expenditures for computing operations. The only residual direct energy cost
attributable to the organisation is end-user device and office connectivity
consumption.

\vspace{0.5em}
\begin{tabularx}{\textwidth}{X r r}
\toprule
\rowcolor{headerrow}
\textcolor{white}{\textbf{Cost Component}} &
\textcolor{white}{\textbf{Annual Cost (\texteuro{})}} &
\textcolor{white}{\textbf{3-Year Total (\texteuro{})}} \\
\midrule
\rowcolor{rowalt}
  Server and infrastructure energy (bundled within SaaS subscription)
  & \texteuro{}0 direct & \texteuro{}0 direct \\
  Office connectivity and end-user devices
  & \texteuro{}150 & \texteuro{}450 \\
\midrule
\rowcolor{palegreen}
  \textbf{TOTAL --- Direct Cloud Energy Cost}
  & \textbf{\texteuro{}150/year} & \textbf{\texteuro{}450} \\
\bottomrule
\end{tabularx}
\captionof{table}{Cloud SaaS Direct Energy Cost Summary --- 3-Year Assessment Period}

\vspace{0.5em}
\textbf{Note:} Server-side energy costs borne by the cloud provider are
accounted for within the SaaS licensing fee, captured under the
subscription cost line of the overall TCO model. This table reflects only
the incremental direct energy costs remaining under the organisation's
operational control.

\section{7.3 Energy Savings Summary}

The net energy cost reduction attributable to the cloud migration over the
three-year assessment period is:

\[
\text{Net Energy Cost Savings}
  = \text{\texteuro{}}12{,}651 - \text{\texteuro{}}450
  = \mathbf{\text{\texteuro{}}12{,}201}
  \quad (96.4\%\ \text{reduction over 3 years})
\]

This \texteuro{}12,201 saving represents a direct and quantifiable input to the
\textbf{TCO comparison} in Section~7.6 of the main report. When
consolidated with hardware CAPEX savings from the elimination of physical
server procurement, reduced IT staffing costs, and lower maintenance
expenditure, the cloud SaaS scenario demonstrates a substantially lower
total cost of ownership over the three-year horizon.

\vspace{0.5em}
\begin{tabularx}{\textwidth}{X r r r}
\toprule
\rowcolor{headerrow}
\textcolor{white}{\textbf{Scenario}} &
\textcolor{white}{\textbf{Annual (\texteuro{})}} &
\textcolor{white}{\textbf{3-Year Total (\texteuro{})}} &
\textcolor{white}{\textbf{Reduction vs.\ On-Premise}} \\
\midrule
\rowcolor{rowalt}
  On-Premise  & \texteuro{}4{,}217 & \texteuro{}12{,}651 & --- \\
  Cloud SaaS  & \texteuro{}150     & \texteuro{}450      & \textbf{\texteuro{}12{,}201 (96.4\%)} \\
\midrule
\rowcolor{palegreen}
  \textbf{Net Saving}
  & \textbf{\texteuro{}4{,}067/year}
  & \textbf{\texteuro{}12{,}201}
  & \textbf{96.4\%} \\
\bottomrule
\end{tabularx}
\captionof{table}{Energy Cost Comparative Summary --- On-Premise vs.\ Cloud SaaS}

\newpage

% ─── REFERENCES ──────────────────────────────────────────────────────────────
\chapter*{References}
\addcontentsline{toc}{chapter}{References}

\begin{itemize}[label={}, leftmargin=1.5em, itemsep=0.3em]
  \item Greenhouse Gas Protocol (2023). \textit{Corporate Value Chain
    (Scope 3) Accounting and Reporting Standard}. World Resources
    Institute \& WBCSD.
  \item International Energy Agency --- IEA (2023). \textit{CO$_2$
    Emissions from Fuel Combustion --- Highlights}. IEA Publications,
    Paris.
  \item Amazon Web Services (2023). \textit{AWS Sustainability Report
    2023}. Available at: \url{https://sustainability.aboutamazon.com}
  \item Accenture (2020). \textit{The Green Behind the Cloud}. Accenture
    Research. Available at:
    \url{https://www.accenture.com/us-en/insights/technology/green-behind-cloud}
  \item European Environment Agency (2023). \textit{Greenhouse Gas
    Emission Intensity of Electricity Generation in Europe}. EEA Report
    No.~16/2023.
  \item Uptime Institute (2023). \textit{Global Data Center Survey Results
    2023}. Uptime Institute, New York.
\end{itemize}

