
% ═══════════════════════════════════════════════════════════════════════════
%  SECTION 8 --- ESG INDICATORS FOR THE PROJECT DASHBOARD
%  ESG Team Contribution
% ═══════════════════════════════════════════════════════════════════════════

\chapter{Section 8 --- ESG Indicators for the Project Dashboard}

\section{Project Dashboard: Purpose and Architecture}

A project dashboard is a structured, real-time monitoring instrument that
consolidates key project metrics into a single, continuously updated
reference point. It provides the project team, steering committee, and
executive stakeholders with immediate, evidence-based visibility into
project performance across all monitored dimensions.

The dashboard for the Green ERP Migration project is organised into
thematic panels corresponding to the principal monitoring domains:
schedule, budget, risk, and ESG performance. This section defines the
\textbf{ESG panel} --- the dedicated sustainability monitoring component
--- specifying the indicators to be tracked, the reporting cadence,
ownership responsibilities, performance targets, and the escalation
thresholds beyond which corrective action is mandated.

\section{8.1 ESG Dashboard KPI Table}

The following table presents the complete set of ESG Key Performance
Indicators (KPIs) assigned to the project dashboard. Each indicator is
characterised by its unit of measurement, monitoring frequency, designated
owner, performance target, and the alert threshold beyond which escalation
procedures are triggered.

\vspace{0.5em}
\begin{longtable}{p{3.0cm} p{1.6cm} p{1.8cm} p{1.9cm} p{2.0cm} p{2.3cm}}
\caption{ESG Dashboard Indicators --- Monitoring and Escalation Framework}
\label{tab:esg-dashboard} \\

\rowcolor{headerrow}
\textcolor{white}{\textbf{Indicator}} &
\textcolor{white}{\textbf{Unit}} &
\textcolor{white}{\textbf{Frequency}} &
\textcolor{white}{\textbf{Owner}} &
\textcolor{white}{\textbf{Target}} &
\textcolor{white}{\textbf{Alert Threshold}} \\
\midrule
\endfirsthead

\rowcolor{headerrow}
\textcolor{white}{\textbf{Indicator}} &
\textcolor{white}{\textbf{Unit}} &
\textcolor{white}{\textbf{Freq.}} &
\textcolor{white}{\textbf{Owner}} &
\textcolor{white}{\textbf{Target}} &
\textcolor{white}{\textbf{Alert}} \\
\midrule
\endhead

\rowcolor{rowalt}
  CO$_2$ Emissions (Scope~2) &
  kg CO$_2$e/month & Monthly & ESG Lead &
  $<$35\,kg & $>$50\,kg \\

  CO$_2$ Emissions (Scope~3, cumulative) &
  kg CO$_2$e & Quarterly & ESG Lead &
  $<$660\,kg total & $>$800\,kg \\

\rowcolor{rowalt}
  Cloud Energy Consumption &
  kWh/month & Monthly & ESG Lead + IT &
  $<$150\,kWh & $>$200\,kWh \\

  PUE (cloud provider) &
  ratio & Quarterly & ESG Lead &
  $\leq$1.15 & $>$1.20 \\

\rowcolor{rowalt}
  E-waste Decommissioned &
  kg & At migration & IT + ESG &
  0\,kg net new & $>$0\,kg \\

  User Satisfaction Score &
  /\,5 & Post-deployment & PM &
  $\geq$4.2\,/\,5 & $<$3.5\,/\,5 \\

\rowcolor{rowalt}
  GDPR Compliance Rate &
  \% compliant & Monthly & Risk Manager &
  100\% & $<$95\% \\

  Training Completion Rate &
  \% & Weekly (rollout) & PM &
  100\% & $<$80\% \\

\rowcolor{rowalt}
  Provider Renewable Energy Share &
  \% & Quarterly & ESG Lead &
  $\geq$65\% & $<$50\% \\

\bottomrule
\end{longtable}

\section{8.2 ESG Reporting Requirements}

Each bi-weekly project status report must incorporate a dedicated ESG
section, comprising the following mandatory components:

\begin{itemize}[label=\textcolor{midgreen}{$\bullet$}]

  \item A \textbf{traffic-light status rating} for each KPI:
    \textcolor{green!60!black}{\textbf{Green}} (on track) /
    \textcolor{orange}{\textbf{Amber}} (at risk, approaching threshold) /
    \textcolor{red}{\textbf{Red}} (alert threshold exceeded ---
    escalation required).

  \item A \textbf{cumulative CO$_2$ emissions chart} presenting actual
    measured emissions against the projected cloud emissions trajectory
    for the same period, enabling trend identification and forecast
    accuracy assessment.

  \item An \textbf{energy consumption trend graph} displaying monthly
    cloud energy usage against the defined target envelope, with
    annotations for any anomalous consumption events.

  \item A \textbf{sustainability performance narrative} of three to five
    sentences, authored by the ESG Lead, summarising overall ESG standing
    for the reporting period and highlighting any material variances or
    emerging risks.

  \item A log of any \textbf{ESG-related risks that have materialised}
    during the reporting period, with cross-reference to the corresponding
    entries in the project Risk Register.

\end{itemize}

\section{8.3 Escalation Procedure}

A structured escalation protocol governs the response to sustained ESG
performance deviations, ensuring that issues are addressed at the
appropriate governance level without delay.

If any ESG indicator exceeds its defined alert threshold for
\textbf{two consecutive reporting periods}, the ESG Lead is required to
escalate the matter formally to the Project Manager. The Project Manager
is then responsible for presenting the issue --- together with a proposed
corrective action plan --- to the Steering Committee at the earliest
available opportunity.

\textbf{GDPR compliance is subject to an enhanced escalation condition:}
any sustained GDPR compliance rate below 95\% constitutes a
\textbf{project stoppage condition (NO-GO trigger)}. In such an event,
the Project Manager must report the non-compliance status to the Board of
Directors immediately, and all project activities involving personal data
processing must be suspended pending independent verification of
compliance restoration.

\newpage

% ─── REFERENCES ──────────────────────────────────────────────────────────────
\chapter*{References}
\addcontentsline{toc}{chapter}{References}

\begin{itemize}[label={}, leftmargin=1.5em, itemsep=0.3em]
  \item Greenhouse Gas Protocol (2023). \textit{Corporate Value Chain
    (Scope 3) Accounting and Reporting Standard}. World Resources
    Institute \& WBCSD.
  \item European Commission (2016). \textit{General Data Protection
    Regulation (GDPR)}. Regulation (EU) 2016/679. Official Journal of
    the European Union.
  \item ISO 27001:2022. \textit{Information Security, Cybersecurity and
    Privacy Protection --- Information Security Management Systems:
    Requirements}. International Organization for Standardization.
  \item ITIL Foundation (2019). \textit{ITIL 4 Foundation}. Axelos
    Global Best Practice.
  \item Uptime Institute (2023). \textit{Global Data Center Survey Results
    2023}. Uptime Institute, New York.
  \item Amazon Web Services (2023). \textit{AWS Sustainability Report
    2023}. Available at: \url{https://sustainability.aboutamazon.com}
\end{itemize}

